Labeled object representation and manipulation with ITK

### 2007-08-27 article/Article.tex
minor fixes in the article
darcs-hash:20070827133851-2fc9d-6e9eb8802bf984a62f3d06d159980098ea89a635.gz

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^2$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du
D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France.}

@@

\section{Acknowledgments}
I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em SpatialObject} class as base class of the {\em LabelObejct} class.

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}}
\authoraddress{{$^1$}INRA, UMR 1198; ENVA; CNRS, FRE 2857, Biologie du
D\'eveloppement et 
Reproduction, Jouy en Josas, F-78350, France.}

@@

\section{Acknowledgments}
I thank Richard Beare for his suggestion to use the run length encoding to represent the binary objects, and Julien Jomier for his help for the choice to {\em not} use the {\em itk::SpatialObject} class as base class of the {\em itk::LabelObejct} class.
